Cell Decompositions for Rank Two Quiver Grassmannians

### 2019-06-11 Grassmannian_cells.tex
Section 3 edits
Proof of Theorem 4.20

\begin{definition}
  For $V\in \Gr(\cH_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$ as this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

@@

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in \Gr(\cH_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
 As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} gives isomorphisms 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and 
  \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
  The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
\qed\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$, and this morphism is unique (up to scalars) when it exists.
    \item For $W\subseteq V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
      Otherwise, $\Ext(P_{m+1}^W,P_{m+1}^V)$ is naturally isomorphic to the quotient of $W^*\otimes (\cH_m/V)$ by the line corresponding to the standard counit $\CC\to W^*\otimes W$, this line degenerates to a point in the case $W\subseteq V$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, therefore $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
  A routine chase using the following pullback diagram confirms the latter holds if and only if $W\subseteq V$.
  \[\xymatrix{
      & 0 \ar[d] & 0 \ar[d] & 0 \ar[d] \\
      0 \ar[r] & K \ar[r] \ar[d] \ar@{}[dr]|(.7){\lrcorner} & P_m\otimes W \ar[d]^{ev_W} \ar[r] & C \ar[r] \ar[d] & 0\\
    0 \ar[r] & P_m\otimes V \ar[r]^{ev_V} & P_{m+1} \ar[r]^{\pi_V} & P_{m+1}^V \ar[r] & 0}\]

@@

The next result establishes some basic homological properties of these translates of preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

In what follows, we will need to carefully understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\]
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\] 
      is generated by the non-split sequence
      \[\xymatrix{0 \ar[r] & \tilde P_{m,j} \ar[r] & \tilde P_{m+1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m+1}^I \ar[r] & 0}.\]
    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subseteq I$, in which case
      \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
    \item For each proper subset $J\subsetneq I$, there is an exact sequence 
      \begin{equation*}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{J,I}} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation*}
      For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{K,I}=\pi_{m+1}^{J,I}\circ\pi_{m+1}^{K,J}$ and $\pi_{m+1}^I=\pi_{m+1}^{J,I}\circ\pi_{m+1}^J$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.2.
  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.3.
  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

@@

To avoid such ambiguities, we introduce the set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item Given a decomposition $I\sqcup\{i\}=\{1,\ldots,n\}$ with $|I|=n-1$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^I\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{& \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[dl] \ar^(.4){\tilde\pi_{m+1}^{\{i\}^c}}[d] & \ar[l] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[dl]\ar^(.4){\tilde\pi_{m,i}^{\{j\}^c}}[d] & \ar[l] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[dl]\\
        \tilde P_{m+1}^J \ar^{\tilde\pi_{m+1}^{J,\{i\}^c}}[r] & \tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}\ar^{\tilde\pi_{m,i}^{\{i\},\{j\}^c}}[r] & \tilde P_{m,i}^{\{j\}^c}\cong \tilde P_{m-1,(i,j)}^{\{j\}}}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $k<m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if and only if $i_1\notin J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $1\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with $i_k\in I$ and $i_1\notin J$, there exist (unique up to scale) surjective maps $\tilde\pi_{m+1}^{\ui,J,I}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$ satisfying:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,J,I}\circ\tilde\pi_{m+1}^{K,J}=\tilde\pi_{m+1}^{\ui,K,I}$ for $K\subsetneq J$;
        \item $\tilde\pi_{m+1-k,\ui}^{I,H}\circ\tilde\pi_{m+1}^{\ui,J,I}=\tilde\pi_{m+1}^{\ui,J,H}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        \item $\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-k,\ui}}=\tilde\pi_{m+1-k,\ui}^I$;
        \item $\tilde\pi_{m+1}^{\ui,J,I}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,\varnothing,I}$ for $\ell<k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

  The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,J,I}:=\tilde\pi_{m+1-k,\ui}^{\{i_k\},I}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_{k-1}\},\{i_k\}^c}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_1\},\{i_2\}^c}\circ\tilde\pi_{m+1}^{J,\{i_1\}^c}.\]
  These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
\qed\end{proof}

>>>>

\begin{definition}
  For $V\in \Gr(\cH_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_{m+1}^V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$ as this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

@@

\begin{lemma}
  \label{le:unique preprojective morphism}
  For $V\in \Gr(\cH_m)$, $m\ge1$, the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional spanned by the natural projection $\pi_{m+1}^V:P_{m+1}\to P_{m+1}^V$.
  Moreover, $\Ext(P_{m+1},P_{m+1}^V)=0$.
\end{lemma}
\begin{proof}
 As $\Hom(P_{m+1},P_m)=\Ext(P_{m+1},P_m)=0$, applying the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} gives isomorphisms 
  \[\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)\]
  and 
  \[\Ext(P_{m+1},P_{m+1})\cong\Ext(P_{m+1},P_{m+1}^V).\]
  Under the first isomorphism, the identity map on $P_{m+1}$ is taken to the projection $\pi_{m+1}^V:P_{m+1}\to P_{m+1}^V$.
  The second isomorphism together with the rigidity of $P_{m+1}$ gives the final claim.
\qed\end{proof}

\begin{lemma}
  \label{le:unique morphisms}
  Consider $V,W\in \Gr(\cH_m)$, $m\ge1$.
  \begin{enumerate}
    \item There exists a morphism $P_{m+1}^W\to P_{m+1}^V$ if and only if $W\subseteq V$, and this morphism is unique (up to scalars) when it exists.
    \item For $W\subseteq V$, we have $\Ext(P_{m+1}^W,P_{m+1}^V)\cong W^*\otimes(\cH_m/V)$.
      Otherwise, $\Ext(P_{m+1}^W,P_{m+1}^V)$ is naturally isomorphic to the quotient of $W^*\otimes (\cH_m/V)$ by the line corresponding to the standard counit $\CC\to W^*\otimes W$, this line degenerates to a point in the case $W\subseteq V$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  We apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\rightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V)\longrightarrow \Ext(P_{m+1}^W,P_{m+1}^V)\rightarrow 0.\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, therefore $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero (hence one-dimensional) if and only if the morphism $-\circ ev_W$ of the above sequence is zero.
  A routine chase using the following pullback diagram confirms the latter holds if and only if $W\subseteq V$.
  \[\xymatrix{
      & 0 \ar[d] & 0 \ar[d] & 0 \ar[d] \\
      0 \ar[r] & K \ar[r] \ar[d] \ar@{}[dr]|(.7){\lrcorner} & P_m\otimes W \ar[d]^{ev_W} \ar[r] & C \ar[r] \ar[d] & 0\\
      0 \ar[r] & P_m\otimes V \ar[r]^{ev_V} & P_{m+1} \ar[r]^{\pi_{m+1}^V} & P_{m+1}^V \ar[r] & 0}\]

@@

The next result establishes some basic homological properties of these translates of preprojective representations.
\begin{lemma}
  \label{le:homdecomposition}
  For $m\geq 1$, the following hold.
  \begin{enumerate}
    \item We have $\Hom(P_m,P_{m+1})\cong\bigoplus\limits_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m+1})$, where each $\Hom(\tilde P_{m,i},\tilde P_{m+1})$ is one-dimensional.
    \item The representations $\tilde P_{m,i}$ are pairwise orthogonal, i.e.\ for $i\neq j$ we have 
      \[\Hom(\tilde P_{m,i},\tilde P_{m,j})=0=\Ext(\tilde P_{m,i},\tilde P_{m,j}).\]
    \item For $j\in\{1,\ldots,n\}$, we have
      \[\Hom(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m+1},\tilde P_{m,j})=0,\quad\Ext(\tilde P_{m,j},\tilde P_{m+1})=0.\]
    \item For each proper subset $I\subsetneq\{1,\ldots,n\}$, there exists a truncated preprojective representation~$\tilde P_{m+1}^I$ fitting into an exact sequence 
      \begin{equation}
        \label{ses1}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I} \tilde P_{m,i} \ar[r]^{ev_I} & \tilde P_{m+1} \ar[r]^{\tilde\pi_{m+1}^I} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation}
      Moreover, $G(\tilde P_{m+1}^I)$ is a truncated preprojective of $K(n)$ for each $I\subsetneq\{1,\ldots,n\}$.
  \end{enumerate}
\end{lemma}
\begin{remark}
  Note that when $I=\varnothing$, it follows from the definition that $\tilde P_{m+1}^I=\tilde P_{m+1}$.
\end{remark}
\begin{proof}
  Part (1) is immediate from Theorem~\ref{covering}.
  Part (2) is also a consequence of Theorem~\ref{covering}.
  Indeed, for $1\leq j\leq n$, we have 
  $$\CC\cong\Hom(P_m,P_m)\cong\bigoplus_{i=1}^n \Hom(\tilde P_{m,i},\tilde P_{m,j}).$$
  But $\Hom(\tilde P_{m,j},\tilde P_{m,j})\cong\CC$ and so we must have $\Hom(\tilde P_{m,i},\tilde P_{m,j})=0$ for $i\neq j$.
  The vanishing of $\Ext(\tilde P_{m,i},\tilde P_{m,j})$ follows in the same manner using that $P_m$ is exceptional.

@@

In what follows, we will need to carefully understand the homological properties of the truncated preprojectives for $\widetilde{K(n)}$.
\begin{lemma}
  \label{le:properties}
  For $m\geq1$ and $I\subsetneq\{1,\ldots,n\}$, the following hold.
  \begin{enumerate}
    \item For $j\in\{1,\ldots,n\}$, we have $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)=0$.  Also, $\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\ne0$ if and only if $j\not\in I$, in which case 
      \[\Hom(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Hom(\tilde P_{m,j},\tilde P_{m+1})\cong\CC.\]
    \item We have $\Hom(\tilde P_{m+1},\tilde P_{m+1}^I)\cong\CC$ and $\Ext(\tilde P_{m+1},\tilde P_{m+1}^I)=0$. 
    \item For $j\in\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^I,\tilde P_{m,j})=0$.
      Also, $\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\ne0$ if and only if $j\in I$, in which case  
      \[\Ext(\tilde P_{m+1}^I,\tilde P_{m,j})\cong\CC\] 
      is generated by the non-split sequence
      \[\xymatrix{0 \ar[r] & \tilde P_{m,j} \ar[r] & \tilde P_{m+1}^{I\setminus\{j\}} \ar[r] & \tilde P_{m+1}^I \ar[r] & 0}.\]
    \item For any $J\subsetneq\{1,\ldots,n\}$, we have $\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\ne0$ if and only if $J\subseteq I$, in which case
      \[\Hom(\tilde P_{m+1}^J,\tilde P_{m+1}^I)\cong\CC\quad\text{and}\quad\Ext(\tilde P_{m+1}^J,\tilde P_{m+1}^I)=0.\]
      In particular, $\tilde P_{m+1}^I$ is an exceptional representation of $\widetilde{K(n)}$.
    \item For each proper subset $J\subsetneq I$, there is an exact sequence 
      \begin{equation*}
        \xymatrix{ 0 \ar[r] & \bigoplus_{i\in I\setminus J} \tilde P_{m,i} \ar[r] & \tilde P^J_{m+1} \ar[r]^{\tilde\pi_{m+1}^{I,J}} & \tilde P_{m+1}^I \ar[r] & 0}.
      \end{equation*}
      For any sequence of proper subsets $K\subsetneq J\subsetneq I$, the quotient maps satisfy $\pi_{m+1}^{I,K}=\pi_{m+1}^{I,J}\circ\pi_{m+1}^{J,K}$ and $\pi_{m+1}^I=\pi_{m+1}^{I,J}\circ\pi_{m+1}^J$.
  \end{enumerate}
\end{lemma} 
\begin{proof}
  Applying $\Hom(\tilde P_{m,j},-)$ to the sequence \eqref{ses1} gives the exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(\tilde P_{m,j},\bigoplus_{i\in I} \tilde P_{m,i}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}) \ar[r] & \Hom(\tilde P_{m,j},\tilde P_{m+1}^I) \ar[r] & 0},\]
  where the final zero follows from Lemma~\ref{le:homdecomposition}.2.
  This also gives an isomorphism $\Ext(\tilde P_{m,j},\tilde P_{m+1}^I)\cong\Ext(\tilde P_{m,j},\tilde P_{m+1})=0$ by Lemma~\ref{le:homdecomposition}.3.
  Now the middle space in the sequence above is one-dimensional while the left-hand space vanishes if and only if $j\notin I$, this proves part (1).

@@

To avoid such ambiguities, we introduce the set
\[A_1^{(k)}:=\{(i_1,\ldots,i_k)\mid i_j\ne i_{j+1}\text{ for $1\le j\le k-1$}\}\subset\{1,\ldots,n\}^k\]
and call the elements of $A_1^{(k)}$ \emph{admissible sequences} of length $k$.
Here we allow $k=0$ and take $A_1^{(0)}$ to consist of only the empty word $\ui=()$.

The following gives an analogue of Lemma~\ref{cor:truncated preprojective isomorphism}.
For $I\subsetneq\{1,\ldots,n\}$, write $I^c=\{1,\ldots,n\}\setminus I$ for the complementary subset.
\begin{lemma}
  \label{le:truncated quotients}
  For $m\ge2$, the following hold:
  \begin{enumerate}
    \item For $i\in\{1,\ldots,n\}$, there is a canonical isomorphism 
      \[\tilde P_{m+1}^{\{i\}^c}\cong\tilde P_{m,i}^{\{i\}}=\tilde P_{m,i}/\tilde P_{m-1,(i,i)}.\]
    \item For any pair $i,j\in\{1,\ldots,n\}$ with $i\ne j$ and any $J\subsetneq\{i\}^c$, there is a commutative diagram
      \begin{equation}
        \label{dia:truncated coherence}
        \xymatrix@R40pt@C60pt{
           \ar[r] \tilde P_{m-1,(i,j)} \ar_(.45){\tilde\pi_{m-1,(i,j)}^{\{j\}}}[d]
          & \ar[r] \tilde P_{m,i} \ar_(.45){\tilde\pi_{m,i}^{\{i\}}}[d] \ar_{\tilde\pi_{m,i}^{\{j\}^c}}[dl] 
          & \tilde P_{m+1} \ar_(.45){\tilde\pi_{m+1}^J}[d] \ar_{\tilde\pi_{m+1}^{\{i\}^c}}[dl]\\ 
          \tilde P_{m-1,(i,j)}^{\{j\}}\cong \tilde P_{m,i}^{\{j\}^c}
          & \tilde P_{m,i}^{\{i\}}\cong\tilde P_{m+1}^{\{i\}^c} \ar_(.4){\tilde\pi_{m,i}^{\{j\}^c,\{i\}}}[l] 
          & \tilde P_{m+1}^J \ar_(.4){\tilde\pi_{m+1}^{\{i\}^c,J}}[l]}
      \end{equation}
    \item For an admissible sequence $\ui\in A_1^{(k)}$, $1\le k< m$, and $J\subsetneq\{1,\ldots,n\}$, the restriction of $\tilde\pi_{m+1}^J:\tilde P_{m+1}\to\tilde P_{m+1}^J$ to $\tilde P_{m+1-k,\ui}$ is injective if $J\subsetneq\{i_1\}^c$ and is zero if $i_1\in J$.
    \item For any admissible word $\ui\in A_1^{(k)}$ with $0\le k< m$ and any proper subsets $I,J\subsetneq\{1,\ldots,n\}$ with~$i_k\in I$ and $i_1\notin J$ if $k\ge1$ or with $J\subsetneq I$ if $k=0$, there exist (unique up to scale) surjective maps~$\tilde\pi_{m+1}^{\ui,I,J}:\tilde P_{m+1}^J\to \tilde P_{m+1-k,\ui}^I$.
      These satisfy the following relations:
      \begin{itemize}
        \item $\tilde\pi_{m+1}^{\ui,I,J}\circ\tilde\pi_{m+1}^{J,K}=\tilde\pi_{m+1}^{\ui,I,K}$ for $K\subsetneq J$;
          \item $\tilde\pi_{m+1-k,\ui}^{H,I}\circ\tilde\pi_{m+1}^{\ui,I,J}=\tilde\pi_{m+1}^{\ui,H,J}$ for $I\subsetneq H\subsetneq\{1,\ldots,n\}$;
        %\item $\tilde\pi_{m+1}^{\ui,\varnothing,I}\Big|_{\tilde P_{m+1-k,\ui}} =\tilde\pi_{m+1-k,\ui}^I$;
        \item $\tilde\pi_{m+1}^{\ui,I,J}\Big|_{\tilde P_{m+1-\ell,\ui_\ell}}=\tilde\pi_{m+1-\ell,\ui_\ell}^{\ui'_\ell,I,\varnothing}$ for $0\le \ell\le k$, where $\ui_\ell:=(i_1,\ldots,i_\ell)$ and $\ui'_\ell:=(i_{\ell+1},\ldots,i_k)$.
      \end{itemize}
  \end{enumerate}
\end{lemma}
\begin{proof}
  The Auslander-Reiten sequence~\eqref{eq:lifted AR sequence} gives rise to the following commutative diagram:
  \[\xymatrix{& & 0\ar[d]& 0\ar[d]&\\
    & & \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]\ar@{=}[r]& \bigoplus_{i\in I} \tilde P_{m,i}\ar[d]&\\
    0\ar[r]&\tilde P_{m-1} \ar[r]\ar@{=}[d] & \bigoplus_{i=1}^n \tilde P_{m,i}\ar[d]\ar[r]\ar@{}[dr]|(.7){\lrcorner} & \tilde P_{m+1}\ar[r]\ar[d]& 0\\
    0\ar[r] &\tilde P_{m-1}\ar[r] &  \tilde P_{m,j}\ar[r]\ar[d] & \tilde P_{m+1}^I\ar[r]\ar[d] & 0\\
  & & 0& 0&}\]
  The image of the inclusion $\tilde P_{m-1}\into \tilde P_{m,j}$ in the bottom row is the subrepresentation $\tilde P_{m-1,(j,j)}\subset\tilde P_{m,j}$ and part (1) follows.

@@

  The diagrams from (2) stitch together to give the following composition, where we suppress the lower isomorphisms in the diagram \eqref{dia:truncated coherence}:
  \[\tilde\pi_{m+1}^{\ui,I,J}:=\tilde\pi_{m+1-k,\ui}^{I,\{i_k\}}\circ\tilde\pi_{m+2-k,\ui_{k-1}}^{\{i_k\}^c,\{i_{k-1}\}}\circ\cdots\circ\tilde\pi_{m,i_0}^{\{i_2\}^c,\{i_1\}}\circ\tilde\pi_{m+1}^{\{i_1\}^c,J}.\]
  These can be seen to satisfy the desired properties from (4) inductively using Lemma~\ref{le:properties}.5 and the commutativity from (2).
\qed\end{proof}
